---
title: "Datathon_Shirley"
author: "Shirley Gui"
date: "5/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1.exploratory analysis
```{r}
#install.packages("dplyr")
library(dplyr)
library(stringr)
library(ggplot2)
library(pROC)

data <- read.csv(file = "~/Desktop/RotmanDatathon/Rotman MMA Summer Datathon (men&women olympic).csv", header = T)

##filter out Canadian team
canada <- data[str_detect(data$team_name,'Canada'),]
canada_woman <- canada[str_detect(canada$team_name,'Women'),]
canada_man <- canada[str_detect(canada$team_name,'Men'),]

canada_woman %>% group_by(event_successful) %>% summarise(n_woman=n()) %>% mutate(rate=n_woman/sum(n_woman))
canada_man %>% group_by(event_successful) %>% summarise(n_man=n()) %>% mutate(rate=n_man/sum(n_man))

canada_woman %>% group_by(period,event_successful) %>% summarise(n_woman=n()) %>% mutate(rate=n_woman/sum(n_woman))
canada_man %>% group_by(period,event_successful) %>% summarise(n_man=n()) %>% mutate(rate=n_man/sum(n_man))


##for event "play"
summary(canada_woman$event_type)
canada_woman %>% group_by(event_type,event_successful) %>% summarise(n_woman=n()) %>% mutate(rate=n_woman/sum(n_woman))
canada_man %>% group_by(event_type,event_successful) %>% summarise(n_man=n()) %>% mutate(rate=n_man/sum(n_man))


canada_shot <- filter(canada, event_type=='Shot')
canada_shot %>% group_by(shot_type) %>% summarise(n=n())  %>% arrange(desc(n))
canada_shot %>% group_by(shot_type,event_successful) %>% summarise(n=n()) %>% mutate(rate=n/sum(n)) %>% arrange(desc(rate))

##shot successful rate for each canadian player
canada_shot %>% group_by(player_name,event_successful)  %>% summarise(n=n()) %>% mutate(rate=n/sum(n)) %>% arrange(desc(rate)) %>% filter(event_successful=="t")


```
1. The successful rate of woman is 0.68, and man is 0.71. Overall men perform slightly better than women.
2. The successful rate for both man and woman is the best at period 4.
3. The "shot" event is especially low at 0.039(woman) and 0.053(man).


```{r}
##compare the performance of Canadian team with all other teams

#(Women) - Olympic Athletes from Russia
woman_russia <- data[str_detect(data$team_name,'Russia'),]
#(Women) - United States
woman_US <- data[str_detect(data$team_name,'United States'),]
#(Women) - Finland
woman_finland <- data[data$team_name=="Olympic (Women) - Finland",]
#(Men) - Switzerland
man_swzl <- data[str_detect(data$team_name,'Switzerland'),]
#(Men) - Czech Republic
man_CR <- data[str_detect(data$team_name,'Czech Republic'),]
#(Men) - South Korea
man_korea <- data[str_detect(data$team_name,'South Korea'),]
#(Men) - Finland
man_finland <- data[str_detect(data$team_name,'(Men) - Finland'),]
#(Men) - Germany
man_germany <- data[str_detect(data$team_name,'(Men) - Germany'),]


rank_success <- data %>% group_by(team_name,event_successful) %>% summarise(n=n()) %>% mutate(rate=n/sum(n)) %>% arrange(desc(rate))
rank_success <- rank_success %>% filter(event_successful=='t')
rank_success$rate = round(rank_success$rate,digits = 3)
rank_success

woman_rank <- rank_success[str_detect(rank_success$team_name,'Women'),]
man_rank <- rank_success[str_detect(rank_success$team_name,'Men'),]


##plot of men teams
area.color=c("coral2","skyblue3", "skyblue3", "skyblue3", "skyblue3","skyblue3")

p1 <- ggplot(data=man_rank, aes(x=rate, y=team_name)) +
  coord_cartesian(xlim = c(0.6, 0.75))+
  geom_bar(stat="identity", width=0.5, fill = area.color)+
  geom_text(aes(label = rate, y = team_name), size = 3.5, col="gray30",hjust=-0.2)+
  theme_minimal()

p1+labs(title = "Event Success Rate of Men Teams",
              x = "Event Success Rate", y = "Team Names")

##plot of woman teams
area.color2=c("skyblue3","skyblue3", "coral2", "skyblue3")

p2 <- ggplot(data=woman_rank, aes(x=rate, y=team_name)) +
  coord_cartesian(xlim = c(0.53, 0.72))+
  geom_bar(stat="identity", width=0.5, fill = area.color2)+
  geom_text(aes(label = rate, y = team_name), size = 4, col="gray30",hjust=-0.2)+
  theme_minimal()

p2+labs(title = "Event Success Rate of Women Teams",
              x = "Event Success Rate", y = "Team Names")




```
- Overall the Canadian Men Team is of best performance among all other men teams. However, the advantage of Canadian Women Team is less dominant, as it ranks the third out of four teams. The Russian Women Team is apparently left behind among all other teams with a successful rate of 0.58




```{r}
#total scores
scores <- data %>% filter(event_type=="Shot",event_successful=="t") %>% group_by(game_name,team_name) %>% count() %>% arrange(desc(game_name))

#unique(data[,"game_name"]) # 17 different games with only 28 observations

index <- scores$game_name %in% c("2019-02-17 - Olympic (Women) - Canada at Olympic (Women) - United States","2019-02-12 - Olympic (Women) - United States at Olympic (Women) - Canada","2018-02-21 - FInland at Canada	Olympic (Men) - Canada","2018-02-19 - Canada - Women at Olympic Athletes from Russia - Women","2018-02-18 - South Korea at Canada","2018-02-11 - Olympic Athletes from Russia - Women at Canada - Women","2018-02-21 - FInland at Canada")
competing_teams <- scores[!index,]

competing_teams_woman <- competing_teams[str_detect(competing_teams$team_name,'Women'),]
competing_teams_man <- competing_teams[str_detect(competing_teams$team_name,'Men'),]


#plot of woman teams
axis_label1 <- c("18/02/13","18/02/14","18/02/21","19/02/14","19/04/06","19/04/13","19/04/14")
p3 <- ggplot(data=competing_teams_woman, aes(x=game_name, y=n, fill = team_name)) +
  coord_cartesian(ylim = c(0,4))+
  geom_bar(stat="identity", width=0.5,position=position_dodge())+
  scale_fill_manual(values=c('coral2','skyblue',"darkseagreen"))+
  theme_minimal()

p3+labs(title = "Comparison of Scores for Woman Games",
              x = "Different Games", y = "Scores")+
  scale_x_discrete(labels=axis_label1)+
  theme(
     axis.text.x=element_text(),
    axis.ticks.x=element_blank())

#plot of man teams
axis_label2 <- c("2018-02-15","2018-02-16","2018-02-23","2018-02-24")
p4 <- ggplot(data=competing_teams_man, aes(x=game_name, y=n, fill = team_name)) +
  coord_cartesian(ylim = c(0,7))+
  geom_bar(stat="identity", width=0.5,position=position_dodge())+
  scale_fill_manual(values=c('coral2','skyblue',"darkseagreen","rosybrown1"))+
  theme_minimal()

p4+labs(title = "Comparison of Scores for Man Games",
              x = "Different Games", y = "Scores")+
  scale_x_discrete(labels=axis_label2)+
  theme(
    axis.text.x=element_text(),
    axis.ticks.x=element_blank())


```
- Lack data:
  "2019-02-17 - Olympic (Women) - Canada at Olympic (Women) - United States":	Olympic (Women) - United States
  "2019-02-12 - Olympic (Women) - United States at Olympic (Women) - Canada":	Olympic (Women) - Canada
  "2018-02-21 - FInland at Canada	Olympic (Men) - Canada": Olympic (Men) - Finland
  "2018-02-19 - Canada - Women at Olympic Athletes from Russia - Women":	Olympic (Women) - Russia
  "2018-02-18 - South Korea at Canada":	Olympic (Men) - South Korea
  "2018-02-11 - Olympic Athletes from Russia - Women at Canada - Women":	Olympic (Women) - Russia
  
- Insights:
1. From 18/02/14 to 19/04/06, the overall performance of U.S Women team has gradually increased.
2. There was a significant improvement for Finland Women team for 18/02/13 and 19/04/13.





#2.weights of importance for events
##Comparison of woman Finland & women Canada team
```{r}
##Game for 18/02/13
df1 <- woman_finland[woman_finland$game_date=="2/13/2018",] %>% group_by(event_type,event_successful) %>% summarise(n=n()) 
df2 <- canada_woman[canada_woman$game_date=="2/13/2018",] %>% group_by(event_type,event_successful) %>% summarise(n=n())

##Game for 19/04/14
df3 <- woman_finland[woman_finland$game_date=="4/13/2019",] %>% group_by(event_type,event_successful) %>% summarise(n=n())
df4 <-canada_woman[canada_woman$game_date=="4/13/2019",] %>% group_by(event_type,event_successful) %>% summarise(n=n())

df1 %>% filter(event_type=="Play") %>% mutate(percentage=n/sum(n)) #70.25%
df2 %>% filter(event_type=="Play") %>% mutate(percentage=n/sum(n)) #68.43%
df3 %>% filter(event_type=="Play") %>% mutate(percentage=n/sum(n)) #72.80%
df4 %>% filter(event_type=="Play") %>% mutate(percentage=n/sum(n)) #80.64%

df1 %>% filter(event_type=="Shot") %>% mutate(percentage=n/sum(n)) #2.17%
df2 %>% filter(event_type=="Shot") %>% mutate(percentage=n/sum(n)) #6.67%
df3 %>% filter(event_type=="Shot") %>% mutate(percentage=n/sum(n)) #9.09%
df4 %>% filter(event_type=="Shot") %>% mutate(percentage=n/sum(n)) #2%

df1 %>% filter(event_type=="Takeaway") 
df2 %>% filter(event_type=="Takeaway") 
df3 %>% filter(event_type=="Takeaway") 
df4 %>% filter(event_type=="Takeaway") 

df1 %>% filter(event_type=="Faceoff")
df2 %>% filter(event_type=="Faceoff")
df3 %>% filter(event_type=="Faceoff") 
df4 %>% filter(event_type=="Faceoff")

```

##Comparison of woman US & women Canada team

```{r}
#based on the results:
#weights	pass 3.23%	shot77.08%	takeaway 13.98%	faceoff 5.70%
```

##weights
```{r}
weigh_pass <- (0.0323+0.031)/2
weigh_shot <- (0.8483+0.7708)/2
weigh_takeaway <- (0.1398+0.077)/2
weigh_faceoff <- (0.0437+0.057)/2
weigh_pass
weigh_shot
weigh_takeaway
weigh_faceoff
```


#3.Models
##'Shot' Model
```{r}
library(rpart)
library(caTools)
library(rpart.plot)
#shot data

shot <- filter(data, event_type=="Shot")
shot <- shot[,c("game_name","period","team_name","player_name","shot_type","situation_type","x_event","y_event","event_successful")]
shot <- shot %>% rename(x=x_event,y=y_event, goal=event_successful,shooter=player_name)
shot['goal'] <- data.frame(lapply(shot['goal'], as.character), stringsAsFactors=FALSE)

#convert "f/t" to binary 0/1
for (i in 1:nrow(shot)){
  if (shot['goal'][i,]=="f"){
    shot['goal'][i,] = 0 
  }
  else {
    shot['goal'][i,] = 1 
  }
}

#top players who have the most successful shots 
shooter <- shot %>% group_by(shooter,goal) %>% summarise(n=n())
shooter %>% filter(goal==1) %>% arrange(desc(n))

#add new variables "shot_dist" "shot_angel"
net <- c(200,85/2)
for (i in 1:nrow(shot)){
  shot$shot_dist[i] <- sqrt((net[1]-shot[i,"x"])^2+(net[2]-shot[i,"y"])^2)
}

#note: r always works wirh radians, not angel; radian=angel*pi/180
#example:tan(45*pi/180); atan(tan(45*pi/180)) /pi*180
for (i in 1:nrow(shot)){
  shot$shot_angel[i] <- atan((abs(net[2]-shot[i,"y"]))/abs(net[1]-shot[i,"x"]))/pi*180
}


shot$goal = factor(shot$goal)
shot$period = factor(shot$period)

shot <- na.omit(shot)

set.seed(100)
split.1 <- sample.split(shot$goal, 0.7)
shot_train <- subset(shot, split.1==TRUE)
shot_test <- subset(shot, split.1==FALSE)

obs_result1 <- shot_test$goal

##1. Logistic model
model1 <- glm(goal ~ shot_dist + shot_angel + shot_type , data=shot_train, family = binomial(link="logit"))
summary(model1)
prob <- predict(model1, newdata=shot_test, type="response")
results.1 <- ifelse(prob>0.5,1,0)
#accuracy rate:
1-(mean(results.1!=obs_result1))  #0.9643963
##Compute roc
res.roc1 <- roc(obs_result1, prob)
plot.roc(res.roc1, print.auc = TRUE) #AUC:0.782


##2. decision tree model
tree <- rpart(goal ~ shot_dist + shot_angel , data=shot, control=rpart.control(cp=.005))
plot(tree, uniform=TRUE, margin=.05)
text(tree)
rpart.plot(tree)

pred_tree <- predict(tree, newdata = shot_test)
results.2 <- ifelse(pred_tree[,"0"]>0.5,0,1)
#accuracy rate:
1-(mean(results.2!=obs_result1)) #0.9659443
##Compute roc
res.roc2 <- roc(obs_result1, pred_tree[,2])
plot.roc(res.roc2, print.auc = TRUE) #AUC:0.710

```


- We built 2 models: logistic regression, decision tree. Based on the AUC and accuracy rate, logistic performs better. So we will use logistic model.
- Based on the logistic model, shot distance and shot angel are significant in determining whether the shot is successful.
- Our next step is to use Canadian Woman data to predict the prob of successful shot based on each player's average distance and angel data.

##. 'Pass' Model
```{r}

##play data (reflect the quality of passes)
pass <- data %>% filter(event_type=='Play')
pass <- pass[,c("game_name","period","team_name","player_name","receiver_name","situation_type","x_event","y_event","receiver_x","receiver_y","event_successful")]
pass <- pass %>% rename(x=x_event,y=y_event, goal=event_successful)
pass['goal'] <- data.frame(lapply(pass['goal'], as.character), stringsAsFactors=FALSE)

##convert "f/t" to binary 0/1
for (i in 1:nrow(pass)){
  if (pass['goal'][i,]=="f"){
    pass['goal'][i,] = 0 
  }
  else {
    pass['goal'][i,] = 1 
  }
}


##add new variables "shot_dist" "shot_angel"
for (i in 1:nrow(pass)){
  pass$distance[i] <- sqrt((pass[i,"receiver_x"]-pass[i,"x"])^2+(pass[i,"receiver_y"]-pass[i,"y"])^2)
}

###note: r always works wirh radians, not angel; radian=angel*pi/180
###example:tan(45*pi/180); atan(tan(45*pi/180)) /pi*180
for (i in 1:nrow(pass)){
  pass$angel[i] <- atan((abs(pass[i,"receiver_y"]-pass[i,"y"]))/abs(pass[i,"receiver_x"]-pass[i,"x"]))/pi*180
}

pass$goal = factor(pass$goal)
pass$period = factor(pass$period)

pass <- na.omit(pass)

set.seed(100)
split.1 <- sample.split(shot$goal, 0.7)
pass_train <- subset(pass, split.1==TRUE)
pass_test <- subset(pass, split.1==FALSE)

##1.logistic model

model2 <- glm(goal ~ distance + angel+x +y+receiver_x+receiver_y  , data=pass_train, family = binomial(link="logit"))
summary(model2)
prob2 <- predict(model2, newdata = pass_test, type="response")
results.3 <- ifelse(prob2>0.5,1,0)
obs_result2 <- as.numeric(as.character(pass_test$goal))

#model <- glm(goal ~., data = pass_train, family = binomial) %>%
  stepAIC(trace = FALSE)

##accuracy:
1-(mean(results.3!=obs_result2))  #0.7340191
##Compute roc
res.roc3 <- roc(obs_result2, prob2)
plot.roc(res.roc3, print.auc = TRUE) #AUC:0.629

##2.decision tree model
tree2 <- rpart(goal~distance + angel + x +y+receiver_x+receiver_y+period+team_name, data = pass_train, method = 'class')

plot(tree2, uniform=TRUE, margin=.05)
text(tree2)
rpart.plot(tree2)

pred_tree2 <- predict(tree2, newdata = pass_test)
results.4 <- ifelse(pred_tree2[,"0"]>0.5,0,1)
##accuracy:
1-(mean(results.4!=pass_test$goal))  #0.7526329
##Compute roc
res.roc4 <- roc(obs_result2, pred_tree2[,2])
plot.roc(res.roc4, print.auc = TRUE) #AUC: 0.566


```
- We built 2 models: logistic regression, decision tree. Based on the AUC and accuracy rate, logistic performs better. So we will use logistic model.
- Based on the logistic, significant variables that determines whether the pass is successful are: distance,angel,x,receiver_x.
- Our next step is to use Canadian Woman data to predict the prob of successful pass based on each player's significant variables.





##shot
```{r}
#Use logistic model to select top 5 shooters in power play situation
#Method: average all probablities of succussful shot for each player
cw_df <- filter(shot, team_name=="Olympic (Women) - Canada")
cw_df$prob_goal <- predict(model1, newdata = cw_df, type="response")
shooters <- cw_df %>% group_by(shooter,situation_type) %>% summarise(prob=mean(prob_goal)) %>% arrange(desc(prob))
shooters

## method min-max normaliazation
min_max <- function(x){(x-min(x))/(max(x)-min(x))}
shooters$prob_norm <- min_max(shooters$prob)

top_shot_names <- c("Haley Irwin","Melodie Daoust","Victoria Bach","Rebecca Leslie","Jamie Lee Rattray")
top_shooters <- filter(cw_df, shooter %in% top_shot_names)[,c("shooter","prob_goal")] %>% arrange(shooter)
library(ggplot2)
p2 <- ggplot(top_shooters, aes(x=shooter, y=prob_goal, fill=shooter))  +geom_boxplot(varwidth = TRUE, alpha=0.2) +
    theme(legend.position="none") 

p2 + labs(x="shooters", y = "predicted successful rate")

```

##pass
```{r}
#Use logistic model to select top 5 possers
#Method: average all probablities of succussful pass for each player
cw_df2 <- filter(pass, team_name=="Olympic (Women) - Canada")
cw_df2$prob_goal <- predict(model2, newdata = cw_df2, type="response")
passers <- cw_df2 %>% group_by(player_name,situation_type) %>% summarise(prob=mean(prob_goal)) %>% arrange(desc(prob))
passers

## method min-max normaliazation
min_max <- function(x){(x-min(x))/(max(x)-min(x))}
passers$prob_norm <- min_max(passers$prob)

top_pass_names <- c("Shannon Szabados","Haley Irwin","Genevieve Lacasse","Ann-Renee Desbiens","Loren Gabel")
top_passers <- filter(cw_df2, player_name %in% top_pass_names)[,c("player_name","prob_goal")] %>% arrange(player_name)

p1 <- ggplot(top_passers, aes(x=player_name, y=prob_goal, fill=player_name))   +geom_boxplot(varwidth = TRUE, alpha=0.2) +
    theme(legend.position="none")
p1+labs(x="passers", y = "predicted successful rate")

top_pass_names <- c("Shannon Szabados","Haley Irwin","Genevieve Lacasse","Ann-Renee Desbiens","Loren Gabel")
top_passers <- filter(cw_df2, player_name %in% top_pass_names)[,c("player_name","prob_goal")] %>% arrange(player_name)

p1 <- ggplot(top_passers, aes(x=player_name, y=prob_goal, fill=player_name))   +geom_boxplot(varwidth = TRUE, alpha=0.2) +
    theme(legend.position="none")
p1+labs(x="passers", y = "predicted successful rate")

```


#4.1 Top Power Play Specialiests

##top PP specialiests 
```{r}
## shooters under power play
shot_pp <- filter(shooters, situation_type == "5 on 4" | situation_type == "6 on 5" |
                    situation_type == "5 on 3" | situation_type == "6 on 4" |
                    situation_type == "4 on 3")  %>% group_by(shooter) %>% summarise(prob_shot=mean(prob), prob_shot_norm=mean(prob_norm)) %>% arrange(desc(prob_shot_norm))
shot_pp$player_name = shot_pp$shooter


sum_shots <- filter(cw_df, situation_type == "5 on 4" | situation_type == "6 on 5" |
                    situation_type == "5 on 3" | situation_type == "6 on 4" |
                    situation_type == "4 on 3") %>% group_by(shooter) %>% 
  summarise(total_shots=n())
filter1 <- median(sum_shots$total_shots)


shot_candidate <- select(filter(sum_shots, total_shots >= filter1), shooter)
colnames(shot_candidate)[1] <- "player_name"
shot_candidate$prob_shot_norm <- "NA"


new_shotpp <- select(inner_join(select(shot_pp, player_name, prob_shot_norm), shot_candidate,
                         by = "player_name"), -prob_shot_norm.y)
colnames(new_shotpp)[2] <- "prob_shot_norm"





## passers under power play
pass_pp <- filter(passers, situation_type == "5 on 4" | situation_type == "6 on 5" |
                    situation_type == "5 on 3" | situation_type == "6 on 4" |
                    situation_type == "4 on 3")  %>% group_by(player_name) %>% summarise(prob_pass=mean(prob), prob_pass_norm=mean(prob_norm)) %>% arrange(desc(prob_pass_norm))



sum_passes <- filter(cw_df2, situation_type == "5 on 4" | situation_type == "6 on 5" |
                    situation_type == "5 on 3" | situation_type == "6 on 4" |
                    situation_type == "4 on 3") %>% group_by(player_name) %>% 
  summarise(total_passes=n())
filter2 <- median(sum_passes$total_passes)


pass_candidate <- select(filter(sum_passes, total_passes >= filter2), player_name)
pass_candidate$prob_pass_norm <- "NA"


new_passpp <- select(inner_join(select(pass_pp, player_name, prob_pass_norm), pass_candidate,
                         by = "player_name"), -prob_pass_norm.y)
colnames(new_passpp)[2] <- "prob_pass_norm"





#final ranks
PP <- merge(new_shotpp, new_passpp, by = c('player_name'))
PP_rank <- PP %>% group_by(player_name) %>% mutate(results = prob_shot_norm*weigh_shot+prob_pass_norm*weigh_pass) %>% arrange(desc(results))

PP_rank[1:5, "player_name"]
```

#4.2 Top Penalty kill Specialiests

##takeaway in PK
```{r}
game <- select(filter(canada_woman,event_type=="Takeaway"), player_name, game_name) %>% group_by(player_name,player_name) %>% distinct(game_name) 

sum_game <- game %>% count(player_name, sort = TRUE)
sum_game

sum_take <- canada_woman %>% filter(event_type=="Takeaway", event_successful=="t") %>% group_by(player_name, situation_type) %>% summarise(n=n()) %>% arrange(desc(player_name)) 

takeaway <- inner_join(sum_take, sum_game, by = "player_name")
takeaway$take_per_game <- takeaway$n.x / takeaway$n.y
colnames(takeaway)[3] <- "sum_of_take"
colnames(takeaway)[4] <- "sum_of_game"
takeaway <- select(takeaway, -sum_of_take, -sum_of_game)


## method min-max normaliazation
min_max <- function(x){(x-min(x))/(max(x)-min(x))}
takeaway$take_per_game_norm <- min_max(takeaway$take_per_game)
takeaway <- takeaway  %>% arrange(desc(take_per_game))
takeaway
```


##top PK Specialiests
```{r}
#takeaway in PK
take_pk <- filter(takeaway, situation_type == "4 on 5" | situation_type == "5 on 6") %>% group_by(player_name) %>% summarise(take_per_game=mean(take_per_game), take_per_game_norm=mean(take_per_game_norm)) %>% arrange(desc(take_per_game), desc(take_per_game_norm))




#pass in PK
pass_pk <- filter(passers, situation_type == "4 on 5" | situation_type == "5 on 6") %>%  group_by(player_name) %>% summarise( prob=mean(prob), prob_norm=mean(prob_norm)) %>% arrange(desc(prob), desc(prob_norm))



sum_passes2 <- filter(cw_df2, situation_type == "4 on 5" | situation_type == "5 on 6") %>% 
  group_by(player_name) %>% summarise(total_passes=n())

filter3 <- median(sum_passes2$total_passes)


pass_candidate2 <- select(filter(sum_passes2, total_passes >= filter3), player_name)
pass_candidate2$prob_norm <- "NA"


new_passpk <- select(inner_join(select(pass_pk, player_name, prob_norm), pass_candidate2,
                         by = "player_name"), -prob_norm.y)
colnames(new_passpk)[2] <- "prob_norm"


#final ranks
PK <- merge(take_pk, new_passpk, by = c('player_name'))
PK_rank <- PK %>% group_by(player_name) %>% mutate(results = take_per_game_norm*weigh_takeaway+prob_norm*weigh_pass) %>% arrange(desc(results))

PK_rank[1:4, "player_name"]
```



